What We Eval in the Shadows

### 2021-08-11 paper/main.tex
Move the subset example

>>>>

The use of \eval with \code{substitute} is a general pattern that we often see
in R packages. It is used to make the interfaces more flexible. For example the
\c{subset}, which selects columns in a data frame, uses it to allow to specify
the selected columns using either the column name or index. For example
\c{subset(df, sel=c(1,B,x))} returns a subset of \code{df} with the first
column, the column named \code{B} and whatever column is at index the variable
\code{x} holds.

It is implemented using \code{eval(substitute(sel), nl, parent.frame())}. The
first argument returns the expression passed to \code{sel}. The second is a
named list that contains the names of the columns from \code{df} and which will
be used to evaluate the expression. The last parameter indicates which
environment should be used to look up bindings not found in \c{nl}.
